\label{chap:voice}
\section{Overview} \label{voice:intro}
This chapter introduces the first argument for a theory of Voice which makes room for an underspecified variant, one which neither requires nor prohibits a specifier. We will first consider morphological marking which is compatible with a variety of verbal forms, namely the template {\tkal}.

As we have already seen briefly in the previous chapter, Hebrew has dedicated active and non-active morphology (a characterization we will refine in the following chapters). Nevertheless, while verbs in {\tnif} are non-active and those in {\thif} are active, verbs in {\tkal} are underspecified with regards to their argument structure. With some roots, the verb might be transitive, (\ref{ex:voice-intro-tr}), with others, unergative, (\ref{ex:voice-intro-unerg}), with others, ditransitive, (\ref{ex:voice-intro-ditr}), and with others still, unaccusative, (\ref{ex:voice-intro-unacc}).
\pex\label{ex:voice-intro-tr}
	\a \begingl
		\gla teo \textbf{taraf} et ha-laxmanja//
		\glb Theo devoured \gsc{ACC} the-bread.roll//
		\glft `Theo devoured the bread roll.'//
	\endgl
	\a \begingl
		\gla ha-balʃan \textbf{katav} et ha-maamar ha-arox//
		\glb the-linguist wrote \gsc{ACC} the-article the-long//
		\glft `The linguist wrote the long article.'//
	\endgl
\xe

\pex\label{ex:voice-intro-unerg}
	\a \begingl
		\gla teo \textbf{rakad} ve-rakad ve-rakad (kol ha-boker)//
		\glb Theo danced and-danced and-danced all the-morning//
		\glft `Theo danced and danced and danced (all morning long).'//
	\endgl
	\a \begingl
		\gla teo \textbf{halax} kol ha-boker//
		\glb Theo walked all the-morning//
		\glft `Theo walked all morning long.'//
	\endgl
\xe

\pex\label{ex:voice-intro-ditr}
	\a \begingl
		\gla teo \textbf{natan} *(le-marsel) et ha-xatif//
		\glb Theo gave to-Marcel \gsc{ACC}  the-snack//
		\glft `Theo gave Marcel the treat.'//
	\endgl
	\a \begingl
		\gla teo \textbf{ʃaal} et ha-sefer me-ha-sifria//
		\glb Theo borrowed \gsc{ACC} the-book from-the-library//
		\glft `Theo borrowed the book from the library.'//
	\endgl
\xe

\pex\label{ex:voice-intro-unacc}
	\a \begingl
		\gla \textbf{nafal} le-teo ha-bakbuk//
		\glb fell to-Theo the-bottle//
		\glft `Theo's bottle fell.'//
	\endgl
	\a \begingl
		\gla ha-bakbuk \textbf{kafa} ba-makpi//
		\glb the-bottle froze in.the-freezer//
		\glft `The bottle froze in the freezer.'//
	\endgl
\xe

I look into these patterns in more depth in Section~\ref{voice:voice}, where I situate them within the current theory of Voice. I then show how this head can be constrained by introducing an agentive modifier which I call {\va} in Section~\ref{voice:va}. Section~\ref{voice:conc} summarizes and outlines how the rest of the chapters in the first part of this book develop the theory.

\section{Voice} \label{voice:voice}
	\subsection{What is Voice?}
In the current neo-Davidsonian tradition, theories of argument structure have adopted a specific way of thinking about internal and external arguments in the syntax, based in large part on the interpretation asymmetries observed by \cite{marantz84} and discussed by \cite{kratzer96}. The theme or patient of the predicate is generated within the VP as the complement of V.\footnote{whether or not internal arguments end up in Spec,VP as in various approaches is immaterial here \citep{johnson91,alexiadouschaefer11wccfl}.} The agent is introduced in the specifier of a higher functional head, which takes the VP as its own complement. Since \cite{kratzer96} it has become common to call this head Voice and to associate it with accusative case licensing, thereby identifying it with causative ``little v'' of \cite{chomsky95}. The basics are given in~(\nextx), slightly modifying \citet[121]{kratzer96}. The relevant compositional functions invoked here are Functional Application and Event Identification. We will also make use of Predicate Modification later on in this book; see \cite{wood15springer} for an accessible introduction. I leave out the semantic types of the arguments.
\pex
	\a Mittie fed the dog.
	\a \Tree
	[.VoiceP\\{λe.Agent(Mittie, e) \& feed(the dog, e)}\\{\textsf{(by Functional Application})}
		[.DP\\\emph{Mittie} ]
		[.{λxλe.Agent(x,e) \& feed(the dog, e)}\\{\textsf{(by Event Identification)}}
			[.Voice\\{λxλe.Agent(x,e)} ]
			[.vP\\{λe.feed(the dog, e)}\\{\textsf{(by Functional Application)}}
				[.v\\{λxλe.feed(x,e)}
					[.\root{\gsc{FEED}} ]
					[.v ]
				]
				[.DP\\\emph{the dog} ]
			]
		]
	]
\xe

I would like to focus on two important points as a segue into the current theory. First, this original formulation does not make any claims regarding a structural difference between agents and causers (e.g.~circumstances, inanimate objects or natural forces). While there have been some attempts to draw a structural difference between the two---at least for certain psychological predicates \citep{bellettirizzi88,harleystone13}---I join the majority of work on argument structure in making no claims to that extent \citep{layering15}. For me, agents are a subset of causers, but this difference is semantic, not syntactic. What this means is that an external argument position (Spec,VoiceP) should be compatible with both agents and causers, but some additional element could force only a narrower, agentive reading. This is we will see already in Section~\ref{voice:va}. I will try to be clear about 

The second point is that as a functional head, Voice might be endowed with different features. In principle, since it licenses a DP in its specifier, it should have the EPP feature [D] \citep{chomsky95}. Once we accept that it has that feature, we can begin to ask what other features it can have, and might these features get checked in the course of the derivation. As recapped in the previous chapter, much recent work in argument structure has explored the possible values of the [$\pm$D] feature on Voice; recent approaches are discussed directly in Chapters \ref{chap:aas} and \ref{i:nie}, once the current theory has been developed in depth. To begin, I will now explain what it means for Voice to be underspecified for this feature.

	\subsection{Underspecified Voice}
This monograph promotes a theory of argument structure in which Voice can have one of three values: [+D], [--D] or underspecified for [$\pm$D]. As foreshadowed in the introductory chapter, the idea is that {\vd} requires an external argument and {\vz} prohibits one. We will focus on what it means for Voice not to have a preference on the matter, thereby accounting for the patterns in (\ref{ex:voice-intro-tr})--(\ref{ex:voice-intro-unacc}).

First, let me define underspecified Voice in (\nextx). All definitions of Voice heads in this chapter and the following ones will take the same form: (a) syntactic definition, (b) semantic denotation, and (c) informal spell-out rule. I give these here and expand upon them in turn.
\pex \textbf{Voice}
	\a A Voice head no specified for a [D] feature. It has no requirements regarding whether its specifier must be filled. In transitive verbs, Voice is the locus of accusative case assignment, either itself by feature checking \citep{chomsky95} or through the calculation of dependent case \citep{marantz91}.
	\a \denote{Voice} = $\begin{cases}
		\lambda e.e & \text{/ \trace~ \{ \root{npl} `\root{\gsc{FALL}}', \root{kpa} `\root{\gsc{FREEZE}}' , \dots \} }\\
		\lambda x \lambda e.Agent(x,e) & \\
		\end{cases}$

%	\denote{Voice} = $\begin{cases}
%		\lambda x \lambda e.Agent(x,e) & \text{/ \trace~\{ \root{axl} `\root{\gsc{EAT}}', \root{ktb} `\root{\gsc{WRITE}}', \root{ntn} `\root{\gsc{GIVE}}',}\\
%			& \text{\root{ʃal} `\root{\gsc{BORROW}}', \root{\gsc{r\dgs{k}d}} `\root{\gsc{dance}}', \root{\gsc{hlx}} `\root{\gsc{WALK}}', \dots\} }\\
%		\lambda e.e & \text{/ \trace~ \{ \root{npl} `\root{\gsc{FALL}}', \root{kpa} `\root{\gsc{FREEZE}}' , \dots \} }
%		\end{cases}$
	\a Voice \lra~{\tkal} \hfill  (with the allomorph {\tpie} to follow in Section \ref{voice:va})
\xe

		\subsubsection{Syntax}
In the current system, the lack of a feature on Voice means that the head is not specified for any syntactic feature constraining Spec,VoiceP. That position can be filled or left unprojected, as far as the Voice head is concerned. In this state of affairs, the expectation is that differences between verbs will result from the requirements of individual roots, rather than anything in the structure. In other words, some roots will give rise to transitive verbs, other roots to unaccusative verbs, and so on.

This is exactly what we find in the template {\tkal}, which spells out Voice. There are no structural restrictions on argument structure in this template: verbs in {\tkal} might be transitive, unergative, ditransitive or unaccusative. Some of the examples in (\ref{ex:voice-intro-tr})--(\ref{ex:voice-intro-unacc} are repeated below with the relevant diagnostics.

In~(\nextx) we see the core transitive verb \emph{taraf}, which requires an internal argument. The accusative/DOM marker \emph{et} must also appear, indicating that this is a transitive construction.\footnote{There is a substantial literature on \emph{et} and what it tracks. I assume for present purposes, rather uncontroversially, that it is only compatible with accusative objects.}
\pex\label{ex:voice-intro-tr2}
	\a 
	\begingl
		\gla teo \textbf{taraf} *(et ha-laxmanja)//
		\glb Theo devoured \gsc{ACC} the-bread.roll//
		\glft `Theo devoured the bread roll.'//
	\endgl
	\a \Tree
	[.VoiceP
		[.\emph{teo} ]
		[.
			[.Voice ]
			[.vP
				[.v
					[.\root{trf} ]
					[.v ]
				]
				[.DP\\\emph{et ha-laxmanja} ]
			]
		]
	]
\xe

Unergative verbs are also possible, as with \emph{rakad} `danced' in~(\nextx). No internal argument is necessary, the event is an activity which can go on over a certain period of time with no concrete telos, and agent-oriented adverbs are possible.
\pex\label{ex:voice-intro-unerg2}
	\a \begingl
		\gla teo \textbf{rakad} ve-rakad ve-rakad (be-mejomanut) (kol ha-boker)//
		\glb Theo danced and-danced and-danced in-skill all the-morning//
		\glft `Theo danced and danced and danced (skillfully) (all morning long).'//
	\endgl
	\a \Tree
	[.VoiceP
		[.\emph{teo} ]
		[.
			[.Voice ]
			[.vP
				[.v
					[.\root{rkd} ]
					[.v ]
				]
			]
		]
	]
\xe

Ditransitive verbs are also possible, as in~(\nextx). We do not need to commit to any specific analysis of ditransitive verbs, so I give a general structure headed by Appl or \emph{p}, a PP-licenser \citep{koopman97,svenonius03,gehrke08phd,wood15springer} I return to in Chapter~\ref{vz:figrefl}.
\pex\label{ex:voice-intro-ditr2}
	\a \begingl
		\gla teo \textbf{natan} *(le-marsel) et ha-xatif //
		\glb Theo gave \gsc{ACC} to-Marcel the-snack//
		\glft `Theo gave Marcel the treat.'//
	\endgl
	\a \Tree
	[.VoiceP
		[.\emph{teo} ]
		[.
			[.Voice ]
			[.ApplP/\emph{p}P
				[.PP\\\emph{le-marsel} ]
				[.
					[.Appl/\emph{p} ]
					[.vP
						[.v
							[.\root{ntn} ]
							[.v ]
						]
						[.DP\\\emph{et ha-xatif} ]
					]
				]
			]
		]
	]
\xe

Lastly, unaccusative verbs are also possible. The two traditional diagnostics are fronting of the verb and the possibility of using a possessive dative, both evident in~(\nextx). I return to discussing these diagnostics in some more depth when we focus on unaccusative verbs in Chapter~\ref{vz:nact}. The tree in~(\anextx b) does not present the final word order, on which see \cite{preminger10}.
\pex\label{ex:voice-intro-unacc2}
	\a \begingl
		\gla \textbf{nafal} le-teo ha-bakbuk//
		\glb fell to-Theo the-bottle//
		\glft `Theo's bottle fell.'//
	\endgl
	\a \Tree
	[.VoiceP
		[.Voice ]
		[.ApplP/\emph{p}P
			[.PP\\\emph{le-teo} ]
			[.
				[.Appl/\emph{p} ]	
				[.vP
					[.v
						[.\root{nfl} ]
						[.v ]
					]
					[.DP\\\emph{he-bakbuk} ]
				]
			]
		]
	]
\xe		

The current analysis captures the underspecified nature of {\tkal} straightforwardly. Since there are no restrictions in the syntax, the root is free to require any interpretation from v and Voice (save for reflexive readings, which are discussed in Chapter~\ref{vz:va:refl}).

%% check database for breakdown by type
		
		\subsubsection{Semantics}
The underspecification of this head---and of the resulting template---can be implemented in the semantics using contextual allosemy of Voice, allowing different meanings to arise in different contexts.\footnote{Chapter~\ref{chap:aas} contains a brief comparison of contextual allosemy with one alternative, namely postulating homophonous heads. There is little to choose between the two options.} Assuming that the causative variant is the elsewhere case, certain roots will be said to require a non-active alloseme of Voice, (\nextx):
\pex \denote{Voice} = 
	\a $\lambda$e.e \phantom{agent(x,e)xxx} / \trace~ \{ \root{npl} `\root{\gsc{FALL}}', \root{kpa} `\root{\gsc{FREEZE}}' , \dots \}
	\a $\lambda$x$\lambda$e.Agent(x,e)
%		 & \text{/ \trace~\{ \root{trf} `\root{\gsc{DEVOUR}}', \root{ktb} `\root{\gsc{WRITE}}', \root{ntn} `\root{\gsc{GIVE}}',}\\
%			& \text{\root{ʃal} `\root{\gsc{BORROW}}', \root{\gsc{r\dgs{k}d}} `\root{\gsc{dance}}', \root{\gsc{hlx}} `\root{\gsc{WALK}}', \dots\} }\\
\xe
		
		
		\subsubsection{Phonology}
While this template is underspecified in the syntax and semantics, the lack of overt heads constraining the structure means that it can be \emph{more} marked in the phonology. The intuition is that if there are no overt affixes, the root will have free reign in the phonology. For example, verbal stems are normally longer than one syllable except for some roots in {\tkal}:
\ex \emph{ba} `came', \emph{ʃav} `returned', \emph{{\texttslig}a{\texttslig}} `appeared'.
\xe

The phonological markedness of this template has been discussed in contemporary work by \cite{ussishkin05} in terms of Emergence of the Unmarked, with similar observations made by \cite{laks11} and \cite{borer13oup,borer15roots}. I will not have much to add on this point here. In Section~\ref{voice:va} below I introduce a modifier which constrains both the semantics and phonology of Voice. The relevant Vocabulary Items can be schematized in~(\nextx).
\pex Voice {\lra}
	\a {\tpie} / {\trace} {\va}
	\a {\tkal}
\xe

The spell-out rules in~(\lastx) provide a crude approximation of how Voice is handled at PF, but it is important to keep in mind that there is no one ``suffix'' {\tkal} or {\tpie} which spells out this head. Rather, there is an intricate morphophonological system of inflectional variants which needs to be taken into account. The full paradigm of {\tpie}, for example, is given by \cite{kastner15nels} as~(\nextx).

\ex
\raisebox{-4.5em}{
\begin{small}
	\begin{tabular}{|l||l|l||l|l||l|l|} \hline
		& \multicolumn{2}{c||}{Past} & \multicolumn{2}{c||}{Present} &  \multicolumn{2}{c|}{Future} \\\hline
		& \gsc{M} & \gsc{F} & \gsc{M} & \gsc{F} & \gsc{M} & \gsc{F} \\\hline\hline
		1\gsc{SG} & \multicolumn{2}{c||}{Xi\dgs{Y}aZ-ti} & me-Xa\dgs{Y}eZ & me-Xa\dgs{Y}eZ-et & \multicolumn{2}{c|}{a-Xa\dgs{Y}eZ/ye-Xa\dgs{Y}eZ}\\\hline
		1\gsc{PL} & \multicolumn{2}{c||}{Xi\dgs{Y}aZ-nu} & me-Xa\dgs{Y}Z-im & me-Xa\dgs{Y}Z-ot & \multicolumn{2}{c|}{ne-Xa\dgs{Y}eZ}  \\\hline\hline
		2\gsc{SG} & Xi\dgs{Y}aZ-ta & Xi\dgs{Y}aZ-t & me-Xa\dgs{Y}eZ & me-Xa\dgs{Y}eZ-et & te-Xa\dgs{Y}eZ & te-Xa\dgs{Y}Z-i\\\hline
		2\gsc{PL} & Xi\dgs{Y}aZ-tem & Xi\dgs{Y}aZ-ten/m & me-Xa\dgs{Y}Z-im & me-Xa\dgs{Y}Z-ot & \multicolumn{2}{c|}{te-Xa\dgs{Y}Z-u}\\\hline\hline
		3\gsc{SG} & Xi\dgs{Y}eZ & Xi\dgs{Y}Z-a & me-Xa\dgs{Y}eZ & me-Xa\dgs{Y}eZ-et & ye-Xa\dgs{Y}eZ & te-Xa\dgs{Y}eZ\\\hline
		3\gsc{PL} & \multicolumn{2}{c||}{Xi\dgs{Y}Z-u} & me-Xa\dgs{Y}Z-im & me-Xa\dgs{Y}Z-ot & \multicolumn{2}{c|}{ye-Xa\dgs{Y}Z-u}\\\hline
	\end{tabular}
\end{small}
}
\xe

A more comprehensive elucidation of this part of the theory can be found in \cite{faust12} and \cite{kastner18nllt}.

	\subsection{Interim summary}
In contrast to the traditional Voice head which introduces an external argument, the current Voice head is underspecified with regards to the EPP feature [D] and does not place any constraints on its specifier. As a result, there are no restrictions on the argument structure of verbs which have only this head. Since every Hebrew verb must be instantiated in one of the seven verbal templates, the appearance of Voice can be traced in the morphology as the template {\tkal}.

In other frameworks, \cite{doron03} does not introduce any special heads in order to account for verbs in {\tkal}. \cite{borer13oup,borer15roots} takes {\tkal} to be a verbalized root, without functional material attaching to it. The two main reasons for this are the wide range of nominalizations possible in this template and the idiosyncratic phonology. I will return to nominalizations in Chapter~\ref{passn:n}, after covering the other variants of Voice, but all three frameworks are compatible in their treatment of the {\tkal}: all allow for {\tkal} to be as idiosyncratic as it needs to be, in the phonology as in the syntax.


\section{Agentive modification} \label{voice:va}
In this section I introduce another syntactic primitive, the agentive modifier {\va}. Strictly speaking, this modifier is not part of the theory of trivalent Voice. As I explain immediately below, we are formalizing an element similar to those which have either been assumed implicitly in other work or been given other names. The reason it is introduced so early on in this book is because it is necessary to capture the full empirical picture. Throughout this book and especially in the first part, we begin each chapter by explaining the theoretical proposal, verifying its immediate predictions, and then expanding the picture by looking at related phenomena in the language. Underspecified Voice and the template {\tkal} have already been addressed, but the behavior of the template {\tpie} indicates that the theory needs to be augmented as I do next. Section~\ref{voice:va:act} sketches the general crosslinguistic phenomenon and Section~\ref{voice:va:heb} formally characterizes the element {\va} in Hebrew.

Let me clarify the terminology. I take causers to be any kind of external argument. Agents are a subset of causes, typically understood as animate and volitional causers. This definition will be relaxed based on the discussion below, where ``agent'' will take on the meaning of ``actor'', ``direct cause'', and the other labels which I take to be more or less identical. I believe that {\va} triggers interpretation in terms of this kind of agency. So, for the rest of this book, when I say \emph{agent} what I mean is a stronger type of causer, a distinction which as far as I can see is vague precisely because it is rooted in the semantics of various kinds of events. The discussion which follows should make these distinctions clear.

	\subsection{Agentive modifiers crosslinguistically} \label{voice:va:act}
%As far as the semantics is concerned, the difference in possible interpretations between~(\lastx a) and~(\lastx b) reduces to whether or not overt {\va} is there to force an agentive reading. \cite{doron03} proposed that this modifier carries the semantics of Action, which is slightly weaker than that of Agent.
A number of recent works on argument and event structure have identified a component of meaning that can be broadly described as agentive, volitional, or (as we will see immediately) a ``direct cause''. In their study of animacy in English, Italian, Greek and Russian, \cite{folliharley08} considered a range of data in which the acceptability of an external argument depends on whether it is \emph{teleologically capable} of causing the event (as opposed to an agency or animacy restriction). Their review identified cases of sound emission, possession, causation, permission and consumption where the licensing conditions on external arguments cannot be understood in terms of animacy, but in terms of whether the internal properties of the external argument can bring about the relevant event.

For example, in Italian causatives, inanimate causers vary with respect to how acceptable they are. A branch is fine, but a storm is not. The explanation is that the branch is a direct causer but the storm is not a proximate enough cause; it is not teleologically capable.\footnote{See \cite{irwin18tlr} for an explication of some teleological properties in terms of body parts.}
\pex
	\a \begingl
		\gla Il ramo ha rotto la finestra//
		\glb the branch has broken the window//
		\glft `The branch broke the window.'//
		\endgl
	\a \begingl
		\gla \ljudge{?}Il vento ha rotto la finestra//
		\glb the wind has broken the window//
		\glft `The wind broke the window.'//
		\endgl
	\a \begingl
		\gla \ljudge{\#}Il temporale ha rotto la finestra//
		\glb the storm has broken the window//
		\glft (int.~`The storm broke the window')\trailingcitation{(Italian, \citealt[195]{folliharley08})}//
		\endgl
\xe		

In other cases, animacy is still the relevant factor within the teleological capability of the relevant argument. Italian \emph{fare}-causatives require the causee to be animate, as in~(\nextx). Similar considerations are familiar from control phenomena as discussed in a range of work from \cite{farkas88} to \cite{zu18phd}.
\pex
	\a \begingl
		\gla Gianni ha fatto rompere la finestra a Maria//
		\glb John has made break the window to Maria//
		\glft `John had Maria break the window.'//
		\endgl
	\a \begingl
		\gla \ljudge{\#}Gianni ha fatto rompere la finestra al ramo//
		\glb John has made break the window to.the branch//
		\glft (int.~`John had the branch break the window)'\trailingcitation{\citep[196]{folliharley08}}//
		\endgl
\xe	

A further dissociation of animacy from agentivity (in the current sense) comes from a study of manner and causation in English by \cite{beaverskoontzgarboden12}, who showed that an animate cause is still not necessarily an agent. The term they use is \emph{actor}, which is employed to discuss events in which an animate causer is or is not responsible for the consequences of its act. For them, causation is compatible with negligence but actorhood (agentivity) is not. That is why even the animate causer in~(\nextx) is not an actor (cf.~\citealt{rappaporthovav14}) :
\ex Kim broke my DVD player, but didn’t move a muscle—rather, when I let her borrow it a disc was spinning in it, and she just let it run until the rotor gave out!\trailingcitation{\citep[347]{beaverskoontzgarboden12}}
\xe

What I would like to highlight is that these kinds of reading can also be triggered by particular morphemes. Moving on to a different empirical domain, recent studies of external arguments in nominalization \citep{sichel10n,alexiadouetal13,ahdout18nom} similarly differentiated agentivity from \emph{direct causation}. The external arguments of argument-structure nominalizations are often taken to exhibit \emph{agent exclusivity}, whereby only agents are possible (see Chapter~\ref{passn:n} for additional background). Examples~(\nextx)--(\anextx) show a typical instantiation of this effect, whereby the animate agent can serve as the external argument of a nominalization, (\nextx), but an inanimate cause cannot, (\anextx).
\pex
	\a \textbf{The Allies} separated East and West Germany.
	\a \textbf{The Allies'} separation of East and West Germany.
\xe
\pex
	\a \textbf{The cold war} separated East and West Germany.
	\a \ljudge{\#}\textbf{The cold war's} separation of East and West Germany.
\xe

\cite{sichel10n} points out, however, that animacy is not always the relevant factor, as observed already in different ways by \cite{pesetsky95} and \cite{marantz97}. The core of her argument is based on natural causers, which are compatible with some nominalizations but not with others (the following judgments are hers). She takes this to mean that direct causation is insufficient if it lacks direct participation.
\pex
	\a The hurricane's \textbf{destruction} of our crops.
	\a The hurricane's \textbf{devastation} of ten coastal communities in Nicaragua
\xe
\ex \ljudge{\#} The approaching hurricane's \textbf{justification} of the abrupt evacuation of the inhabitants
\xe

\cite{alexiadouetal13,alexiadouetal13jcgl} build on \citeauthor{sichel10n}'s proposal and propose that depending on the language and construction, the restriction can depend on either agentivity or direct participation.

Syntactic environments other than nominalization can give rise to similar effects. There are cases where a specific, overt morpheme can be identified as triggering these agentivity-like effects. I mention two here, before we return to a similar phenomenon in Hebrew which I attribute to the element {\va}.

In their studies of the prefix \emph{afto-} in Greek, \cite{alexiadouafto} and \cite{spathasetal15} identified it as an \emph{anti-assistive} modifier, triggering agentive readings regardless of syntactic category, (\nextx).
\pex Agentive readings of \emph{afto-} \citep[61]{alexiadouafto}:
	\a \emph{afto-katastrefome} `self-destroy' (v.)
	\a \emph{afto-kritiki} `self-criticism' (n.)
	\a \emph{afto-didaktos} `self-educated' (a.)
\xe

Given its meaning and its similarity to an analytic paraphrase, (\nextx), \cite{spathasetal15} propose the denotation in~(\anextx).
\pex \citep[63--64]{alexiadouafto}
	\a \begingl
		\gla O Janis katigori-\textbf{te}//
		\glb the John accuses-\gsc{NACT}//
		\glft `John is accused.'//
	\endgl
	\a \begingl
		\gla O janis katigori \textbf{ton} \textbf{eafto} \textbf{tu}//
		\glb the John accuses the self his//
		\glft `John accuses himself.'//
	\endgl
	\a \begingl
		\gla O janis \textbf{afto}-katigori-\textbf{te}//
		\glb the John self-accuse-\gsc{NACT}//
		\glft `John accuses himself.'//
	\endgl
\xe
\ex \denote{\emph{afto}$_{\text{anti-assistive}}$} = $\lambda$f$\lambda$y$\lambda$e.f(y,e) \& $\forall$e'$\forall$x.(e'$\le$e \& Agent(x,e')) $\rightarrow$ x=y \hfill \citep[1335]{spathasetal15}
\xe

Additional elaboration on these complex constructions can be found in these works previous work cited therein. The technical conclusion is that \emph{afto-} is an adjunct which attaches to Voice, triggering agentive meaning.

A comparable (although still distinct) phenomenon can be found in Tamil, were the suffix -\emph{koɭ} adds ``affective semantics'' which are otherwise hard to pin down. \cite{sundaresanmcfadden17} discuss the difference in meaning between verbs with and without -\emph{koɭ} as one of ``affectedness'' in a way that can be exemplified using the examples in~(\nextx). With -\emph{koɭ}, the event affects the agent.
\pex
	\a \begingl
	\gla Mansi paal- æ uutt- in- aaɭ//
	\glb Mansi milk \gsc{ACC} pour.\gsc{TR} Past \gsc{3SG.F}//
	\glft `Mansi poured the milk.'//
	\endgl

	\a 	\begingl
	\gla Mansi paal- æ uutti- \textbf{kko-} ɳɖ- aaɭ//
	\glb Mansi milk \gsc{ACC} pour.\gsc{TR} \gsc{koɭ} Past \gsc{3SG.F}//
	\glft `Mansi poured the milk for herself.' (Reading 1)\\
		`Mansi poured the milk on herself.' (Reading 2)//
	\endgl
\xe

As \citet[165]{sundaresanmcfadden17} put it, ``the end result of some event comes back to affect one of the arguments of that same event'', where the relevant argument is the external argument if there is one, otherwise the internal one (as with unaccusatives). In any case, the semantics of -\emph{koɭ} are such that it forces some kind of agent-oriented reading at least in clauses with external arguments.

Where does this cross-linguistic review leave us? The pretheoretical picture which emerges from these works is that natural language has a way of making a fine-grained distinction between different degrees of ``direct participation'' or agentivity. To the extent that this triggering of agentive semantics is the same phenomenon across languages---and this is an assumption I am making here---it seems highly unlikely that it has the same syntactic underpinnings in all of these cases. A more appropriate explanation would be given in semantic terms (that is, within the denotation of certain morphemes) or in pragmatic terms (world knowledge). As alluded to above, it seems clear that in at least some cases the effect is clearly grammatical, i.e.~should be encoded in the semantics of individual syntactic elements directly, as with agent exclusivity in nominalizations, the anti-assistive modifier in Greek and the affective modifier in Tamil.


	\subsection{\va} \label{voice:va:heb}
A similar phenomenon can be found in Hebrew. It is not part of the trivalent theory of Voice but does interact with it, so I provide a formalization here as the root {\va} which enforces agentive (or Agent-like) readings. Concretely, I assume that {\va} attaches to Voice and triggers its agentive alloseme (following \citealt{doron03,doron14adj}). In the morphophonology we get the templates {\tpie} and {\thit}, as I return to momentarily.
\pex {\va}:
	\a A modifier which attaches to Voice.
	\a \denote{Voice} = $\lambda$e$\lambda$x.e \& \text{Agent}(x,e) / \trace~\va
	\a Voice {\lra} {\tpie} / {\va} {\trace}
	\a {\vz} {\lra} {\thit} / {\va} {\trace}
\xe

To understand the syntax-semantics of {\vz}, consider the two pairs in~(\ref{ex:va-piel1})--(\ref{ex:va-piel2}). In the (a) examples, both agent and causes are possible. In~(\ref{ex:va-piel1}b), only the agent is possible, whereas in~(\ref{ex:va-piel2}b) the external argument must be interpreted as participating in the event itself. The (a) examples have the verb in {\tkal}, the (b) examples in {\tpie}.

\pex \label{ex:va-piel1}
	\a \begingl
		\gla \emph{\{}\cmark~ha-jeladim / \cmark~ha-tiltulim ba-argaz\emph{\}} \textbf{ʃavr}-u et ha-kosot//
		\glb \phantom{\{\cmark~}the-children {} \phantom{\cmark~}the-shaking in.the-box \textbf{broke.\gsc{SMPL}}-\gsc{PL} \gsc{ACC} the-glasses//
		\glft `\{The children / Shaking around in the box\} broke the glasses.'//
		\endgl
	
	\a \begingl
		\gla \emph{\{}\cmark~ha-jeladim / \xmark~ha-tiltulim ba-argaz\emph{\}} \textbf{ʃibr}-u et ha-kosot//
		\glb \phantom{\{\cmark~}the-children {} \phantom{\xmark~}the-shaking in.the-box \textbf{broke.\gsc{INTNS}}-\gsc{PL} \gsc{ACC} the-glasses//
		\glft `\{The children / *Shaking around in the box\} broke the glasses to bits.' \trailingcitation{\citep[20]{doron03}}//
		\endgl
\xe

\pex \label{ex:va-piel2}
	\a \begingl
		\gla ha-xelbon \textbf{ja{\texttslig}ar} ba-guf nogdanim//
		\glb the protein produced.\gsc{SMPL} in the body antibodies//
		\glft `The protein produced antibodies in the body.'//
	\endgl
	
	\a \begingl 
	\gla ha-xelbon \textbf{ji{\texttslig}er} ba-guf nogdanim//
	\glb the protein produced.\gsc{INTNS} in the body antibodies//
	\glft `The protein manufactured antibodies in the body.' \trailingcitation{\citep[21]{doron03}}//
	\endgl
\xe

Since this phenomenon appears to be semantic in nature, as discussed in the previous section (rather than demonstrably syntactic), I formalize it in Hebrew using {\va} (\citealt{doron03} uses a syntactic head $\iota$; see Chapter \ref{vz:others:ed} on some differences between the theories). As a root, this element has phonological and semantic content but no syntactic requirements. Not much hinges on whether this element is a root or a functional head in this language; I take the simple view that it has no syntactic influence, and so is root-like. The question of what other such ``underspecified'' roots might exist in natural language remains an open one for further crosslinguistic research.

The phonological consequences of {\va} will not be explored here in depth. What is important to note is that it is phonologically overt: not only does it trigger a change in vowels, it also blocks a phonological process of spirantization whereby /p/, /b/ and /k/ spirantize to [f], [v] and [x] postvocalically \citep{adam02,temkinmartinez08wccfl,temkinmartinzemuellner16,gouskova12nllt}. An example of this process can be found directly above in~(\ref{ex:va-piel1})a--b), where /b/ spirantizes to [v] after a vowel except if {\va} is also in the structure. See \cite{kastner18nllt} for the details.

Let us now expand the empirical view a bit more: what readings does {\va} make available? The template {\tpie}---made up of a root, v, {\va} and Voice---is traditionally called the ``intensive'', but it can also house pluractional verbs, (\nextx d--f), and various others, (\nextx g--i):
\ex\label{ex:voice:piel-meanings}Pretheoretical classification of some verbs in \tpie:\\
	\begin{tabular}{lll|ll|ll}
	& & & \multicolumn{2}{c|}{\tkal} &  \multicolumn{2}{c}{\tpie}\\\hline
	\multirow{3}{*}{Intensive} & a.& \root{ʃbr} & ʃavar & `broke' & ʃiber & `broke to pieces'\\
		& b.& \root{j{\texttslig}r} & ja{\texttslig}ar & `produced' & ji{\texttslig}er & `produced'\\
	    & c.& \root{'kl} & axal & `ate' & ikel & `corroded, consumed'\\\hline

 	\multirow{3}{*}{Pluractional} & d.& \root{hlx} & halax & `walked' & hilex & `walked around'\\
 	    & e.& \root{r\dgs{k}d} & rakad & `danced' & riked & `danced around'\\
  	    & f.& \root{\dgs{k}fts} & kafats & `jumped' & kipets/kiftsets & `jumped around'\\\hline

  		\multirow{3}{*}{Non-derived} & g. & \root{tps} & \multicolumn{2}{c|}{---} & tipes & `climbed'\\
	    & h. & \root{ltf} & \multicolumn{2}{c|}{---} & litef & `petted'\\
		  & i. & \root{\dgs{k}bl} & \multicolumn{2}{c|}{---} & kibel & `received'\\
	\end{tabular}
\xe

We will next touch on pluractional readings and underived verbs, before concluding.

		\subsubsection{Pluractionality} \label{voice:va:heb:plural}
One possible way to describe the semantics of {\va} is by extended reference to pluractionality. The intuition as is follows. Assume that {\va} is a pluractional (and perhaps also agentive) affix. Building on recent work by \cite{henderson12phd,henderson17nllt}, pluractionality can be seen as a way of pluralizing an event. This pluralization can hold spatially as well as temporally. For the forms in~(\ref{ex:voice:piel-meanings}a--b), the underlying verb in {\tkal} has a direct object. The corresponding pluralized events in {\tpie} can be individuated with respect to the direct objects: many broken pieces in (\ref{ex:voice:piel-meanings}a), many different simultaneous corrosions of parts of the material's surface in (\ref{ex:voice:piel-meanings}c). This extension is admittedly less obvious for ``production'' in~(\ref{ex:voice:piel-meanings}b). \cite{greenberg10} makes a similar claim for verbs in {\tpie} that are derived from reduplicated roots.

For the ``pluractional'' forms in (\ref{ex:voice:piel-meanings}d)--(\ref{ex:voice:piel-meanings}f), the underlying verbs in {\tkal} are unergative. The pluralizing operation has no direct object to operate on, and so it pluralizes the spatio-temporal event itself in {\tpie}.

Lastly, in (\ref{ex:voice:piel-meanings}g)--(\ref{ex:voice:piel-meanings}i) there is no underlying form and hence nothing to pluralize.

The database of verbs we are employing contains over 900 forms in {\tpie}, so this line of inquiry faces a serious amount of empirical corroboration. A number of potential counterexamples can be conjured up fairly easily. These are cases where the alternation does not plausibly result in a plural event:
\pex
	\a \emph{lamad} `learned' $\sim$ \emph{limed} `taught'
	\a \emph{ra{\texttslig}a} `wanted' $\sim$ \emph{ri{\texttslig}a} `satisfied'
\xe

In the examples in~(\lastx) the event does not entail change of state, unlike with breaking and eating/corroding. So perhaps there is a tripartite division of roots to be made, as follows:
\pex
	\a \textbf{Other-oriented roots (change of state):} pluralization of the object.
	\a \textbf{Self-oriented roots:} pluralization of the spatio-temporal aspects of the event.
	\a \textbf{Other cases:} no pluralization.
\xe

Since our current focus is not on the lexical semantics of root classes and how they integrate into the syntax, I will leave proper testing of the hypothesis in~(\lastx) for future work. Evaluating this proposal will need to proceed along the lines laid out above, testing whether each root instantiated in this template does indeed fit into one of the three cases in~(\lastx).


		\subsubsection{Underived forms} \label{voice:va:heb:underived}
A number of verbs in {\tpie} would presumably stretch the notion of ``agentivity'' to the point where such a definition is no longer tenable. In the examples in~(\nextx), the verb can hardly be described as agentive since the subject is inanimate, while in~(\anextx) the subject is animate but non-volitional. These verbs are compatible with agentive subjects as well, but clearly do not require them.
\pex
  \a \begingl
    \gla \underline{ha-midgam} \textbf{ʃikef} et to{\texttslig}ot ha-emet//
    \glb the-poll reflected.\gsc{INTNS} \gsc{ACC} results.\gsc{CS} the-truth//
    \glft `The polls (correctly) reflected the results.'//
  \endgl
    
  \a \begingl
    \gla be-ri{\texttslig}a axat \underline{ha-ʃaon} ʃel garmin kimat \textbf{diek} kaaʃer he{\texttslig}ig stia kimat xasrat maʃmaut ʃel axuz ve-k{\texttslig}at//
    \glb in-run one the-watch of Garmin almost was.accurate.\gsc{INTNS} when showed deviation almost devoid.of meaning of percent and-little//
    \glft `In one run, the Garmin watch was precise as it showed an almost insignificant deviation of just over one percent.'\trailingcitation{\url{www.haaretz.co.il/sport/active/.premium-1.2309128}}//
  \endgl

  \a \begingl
    \gla \underline{ha-xom} \textbf{ʃibeʃ} l-i et ha-medidot//
    \glb the-heat disrupted.\gsc{INTNS} to-me \gsc{ACC} the-measurements//
    \glft `The heat messed up my measurements.//
  \endgl
\xe

\ex \begingl
  \gla \underline{hu} \textbf{kibel} maka xazaka ba-regel//
  \glb he received.\gsc{INTNS} hit strong in.the-leg//
  \glft `He got hit hard in the leg.'//
  \endgl
\xe

In these examples an external argument is still required, regardless of whether it can felicitously be called an Agent or not. What these examples show is that a rigid denotation of {\va} is difficult to specify, beyond some general notion of a direct cause. I believe it is significant, though, that the verbs in~(\blastx)--(\lastx) do not have correspondents in {\tkal}. That is, they are not derived by adding {\va} to an existing VoiceP or via some process of causativization. They would fit with the underived group of~(\ref{ex:voice:piel-meanings}: \emph{ʃikef} $\nless$ *\emph{ʃakaf}, \emph{diek} $\nless$ *\emph{dajak}, \emph{ʃibeʃ} $\nless$ *\emph{ʃabaʃ}, and \emph{kibel} $\nless$ *\emph{kabal}. They are derived when {\va} selects the alloseme of the root directly without having to agentivize a verb in Voice/{\tkal}. If {\va} really is a root rather than a functional head, its partially unpredictable contributions to the meaning of the verb are not unexpected.


\section{Conclusion and outlook} \label{voice:conc}
This chapter began to unfold the theory of trivalent Voice by examining the workings of underspecified Voice in Hebrew, as well as the agentive modifier {\va}. Underspecified Voice does not impose any strict constraints in the syntax but is nevertheless traceable in the morphophonology. It is compatible with whatever argument structure the root allows.

The modifier {\va}, while not part of the theory of trivalent Voice, is a necessary part of any theory of Hebrew morphology. It enforces certain agentive or agentive-like readings which, I have argued, can be found in various other languages as well.

The next chapters in Part I probe the different possible values of Voice. In Chapter~\ref{chap:vz} we will see what happens when Voice is endowed with a [--D] feature, prohibiting the merger of DPs in its specifier. The result will be a structure that allows anticausatives and, in some cases, reflexives of different kinds. In Chapter~\ref{chap:vd} we will see the consequences of a [+D] feature appearing on Voice, requiring its specifier to be filled. And in Chapter~\ref{chap:passn} we will see how these Voice heads interact with passiviziation, nominalization and adjectivization.
